\documentclass[a4paper]{article}

% Import some useful packages
\usepackage[margin=0.5in]{geometry} % narrow margins
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage{minted}
\usepackage{amsmath}
\usepackage{xcolor}
\definecolor{LightGray}{gray}{0.95}

\title{Peer-review of assignment 5 for \textit{INF3331-erlenwe}}
\author{Reviewer 1, bartasv, {bartasv@uio.no} \\
 		Reviewer 2, danieen, {danieen@uio.no} \\
		Reviewer 3, yast, {yast@uio.no}}

\begin{document}
\maketitle

\section{Review}\label{sec:review}

Specify the system (Python version, operating system, ...) that was used for the review. \newline
Python: 3.0				Operating system: macOS Sierra (10.12)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{General feedback}
The code needs more documentation. This will make it easier for us, the reviewers, to understand what you intend to accomplish with your code.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 5.1: Syntax highlighting}
We couldn't run highlighter.py and we don't understand why you used json.

\begin{minted}[bgcolor=LightGray, linenos, fontsize=\footnotesize]{python}
Traceback (most recent call last):
  File "highlighter.py", line 4, in <module>
    from colors import color
ImportError: No module named 'colors'
\end{minted}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 5.2: Python syntax} \label{sec:assignment5.2}
Again: we don't understand why you used json.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 5.3: Syntax for your favorite language}
No answer for this programming part.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 5.4: Syntax for your second favorite language}
No answer for this programming part.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 5.5: superdiff}
The code is working as expected, but it isn't documented at all. This sample of your code: \newline
\begin{minted}[bgcolor=LightGray, linenos, fontsize=\footnotesize]{python}
for i in range(len(original) + 1):
    row = []
    for j in range(len(modified) + 1):
        row.append(0)
    matrix.append(row)
\end{minted}
\newline could have been written in one line: \newline
\begin{minted}[bgcolor=LightGray, linenos, fontsize=\footnotesize]{python}
matrix = [[0 for i in range(len(original)+1)] for j in range(len(modified)+1)]
\end{minted}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 5.6:  Coloring diff}
No answer for this programming part.


\bibliographystyle{plain}
\bibliography{literature}

\end{document}
